### 2021-02-16 main.tex
Add diagrams for Mayer-Vietoris

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

\newcommand{\im}{\mathrm{im}}
\begin{document}
	\begin{theorem}
		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists $U$, an open set containing $V$ such that $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$. Then, $\im \big(H_\bullet(V \cap Y) \to H_\bullet(U)\big) = 0$ is finitely generated.
	\end{theorem}	
\end{document}

>>>>

\documentclass{amsart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{tikz-cd}

@@

\newcommand{\im}{\mathrm{im}}
\newcommand{\Z}{\mathbb{Z}}

\begin{document}
	What we want to prove:
	\begin{theorem}
		Let $Y \subset X$ be a pair of compact Hausdorff spaces such that for any $p \in Y$ and any open neighborhood $V$ of $p$ in $X$ there exists an open neighborhood $U \subset V$ of $p$ such that $\im \big(\widetilde H_\bullet(U \cap Y) \to \widetilde H_\bullet(V)\big) = 0$. Then, $\im \big(H_n(Y) \to H_n(X)\big)$ is finitely generated for every $n$.
	\end{theorem}

	An example to keep in mind:
	$Z = \left\{\frac{1}{n}\ |\ n \geq 0\right\} \cup \{0\} \subset \mathbb R$ is Hausdorff and compact with infinite 0-homology.

	A diagram to keep in mind
	\begin{equation}
	\begin{tikzcd}
	\Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \arrow[r, "0"] & \Z^{\infty} \arrow[r, "1"] & \Z^{\infty} \\
	\Z^{\infty} \arrow[r, "1"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[r, "1"] \arrow[u, "1"] & \Z^{\infty} \arrow[r, "0"] \arrow[u, "0"] & \Z^{\infty} \arrow[u, "0"]
	\end{tikzcd}
	\end{equation}

	Consider the following general diagram
	\begin{equation}
	\begin{tikzcd}
	A_1 \arrow[r, "s_1"] & A_2 \arrow[r, "s_2"] & B \arrow[r, "t_1"] & C_1 \arrow[r, "t_2"] & C_2 \\
	X_1 \arrow[r, "g_1"] \arrow[u, "0"] & X_2 \arrow[r, "g_2"] \arrow[u, "0"] & Y \arrow[r, "h_1"] \arrow[u, "f"] & Z_1 \arrow[r, "h_2"] \arrow[u, "0"] & Z_2 \arrow[u, "0"]
	\end{tikzcd}
	\end{equation}
\end{document}
